\TITLE

### 2023-02-07 paper/content.tex
add support for two columns

\section{Introduction}
\label{sec:introduction}
Service providers (SPs) like lawyers, laboratories, auditors, or banks, to provide services, require data that is often associated with the user identity.

@@

% SB START emphasise 
The problem amplifies when personal information is linked to biological materials like DNA, saliva, or blood, or legal documents like contracts, or wills.

@@

The privacy guarantee of personal information is often based merely on trust assumptions and the security of the IT system. However, most SPs do not need the personal information for any other reason than payment or communication, which should be considered secondary compared to actual service provision.

It would be desirable for the user to keep his or her identity private while still receiving the service. This could lead to reduced trust that users have to put in SPs and less responsibility borne by SPs.

@@

Especially %celebrities, politicians, and %js powtorka
public figures are prone to this kind of problem as such precedent can negatively influence their future career.

@@

Our protocol allows taking such services anonymously, eliminating the strong trust assumption put on the service provider's (e.g., laboratory) IT system.
\item People willing to take risky business activities may be willing to receive the risk estimation and prediction of possible personal repercussions of such action.

By exposing our identity we trust that the lawyer will not use that information for harmful actions.

Our protocol would allow taking such advice anonymously, eliminating the strong trust assumption put on the lawyers and their IT systems.
\end{itemize}

%SB GOAL
In this work, we research the possibility of providing services without the collection of personal information.

@@

Our review of the state of the art indicates that none of the current systems is sufficient to achieve the desired goal. Therefore, we propose a protocol for anonymously provisioning services that require the delivery of physical materials. In case of dispute, either due to exceeding deadlines or providing an incorrect result, the customer can disclose the whole interaction and prove to justice the misbehavior of the SP.

To achieve these objectives, we use:
\begin{itemize}
    \item Blockchain (aka message board), to achieve fairness, i.e., as a means for proving that certain actions took place at a certain moment without the trusted third party (TTP).
    \item Anonymous payment methods, like cash or privacy-preserving cryptocurrencies, allow customers to pay for services anonymously.
    \item Content-addressable decentralized storage network (e.g., IPFS) to anonymously provide results to customers together with a provable storage network (e.g., Filecoin) to guarantee that the results are available to the customer even in case of the SP denial of service. 
    \item Cryptography
    \begin{itemize}
        \item Symmetric encryption, to encrypt and decrypt results published on the public networks.
        \item Public-key cryptography, and Diffie-Helman key exchange (DHKE) to derive shared secrets for symmetric encryption.
        \item Digital signatures, to achieve authentication and non-repudiation of actions. 
    \end{itemize}

@@

%\paragraph{Contributions}
%We contribute to the state of the art by:
The contribution of our paper is:
\begin{itemize}
\item proposing a novel protocol that:
  \begin{itemize}
  \item allows \textbf{anonymous} service provision, i.e., the service provider does not need to collect any personal information from the customer.
  \item achieves \textbf{fairness} by carefully designing the protocol as an interactive non-cooperative game, in which the SP remains in an advantageous position and the customer in a disadvantageous one with the option to start a dispute in case the SP misbehavior.
  \item \textbf{does not rely on centralized TTP}, but uses decentralized blockchain and distributed content-addressable storage network.
  \item abstracts the customers from the blockchain technology used underneath, allowing the use of our protocol for \textbf{non-technical users}.
  \item allows the \textbf{delivery of physical materials}, which was rarely addressed by other researchers or based on strong and unpractical assumptions.
  \item guarantees the \textbf{remote availability of the results}, even in case of the SP denial of service.
  \end{itemize} 
\item Systemise often misused definitions of anonymity, pseudonymity, linkability, and traceability.
\item Proposing a framework for analyzing fairness analysis in fair-exchange protocols.
\item Discuss the possible improvements to the protocol with the use of secure computation, self-sovereign identities, zero-knowledge proofs, and blockchain-based dispute resolution mechanisms.
\end{itemize}

@@

%\paragraph{Organisation}
The rest of this paper is organized as follows.
In section~\ref{sec:related-works} we review related works. 
Then, in section~\ref{sec:building-blocks} we discuss the building blocks of a dispute resolution system, blockchain as a message board, fairness, payment for services, storage network, result availability, anonymity, and confidentiality.
Section~\ref{sec:protocol} describes how the protocol works in detail.
Section~\ref{sec:fairness-analysis} provides a fairness analysis of the proposed protocol.
In Section~\ref{sec:experiments} we present the implementation of the protocol and results of our experiments.
Section~\ref{sec:discussion} discuss possible improvements in terms of crowd-sourced dispute resolution or dispute avoidance, self-sovereign identities (SSI), anonymous delivery, and formal verification.
Finally, section~\ref{sec:conclusion} concludes the paper.

\section{Related Works}\label{sec:related-works}
In this section, we review related works on fair exchange, anonymous, and physical delivery protocols. Then we outline the main differences between our protocol and the existing ones.

\subsection{Fair exchange, physical delivery}
The most common application of fair exchange protocols is e-commerce. A typical transaction involves a seller and a buyer, who exchange money for a physical product such as a smartphone. To protect themselves, a seller would want to receive the funds prior to sending the product, while a buyer would want to receive the product prior to paying. The fairness of the protocol should guarantee that either both parties obtain the goods, or they both obtain nothing.

@@

\begin{itemize}
    \item there exists a trusted third party (TTP) and trusted delivery agent which does not misbehave or collude with any party;
\end{itemize}

@@

\begin{table}
\newcommand{\YES}{\cellcolor{green!50}Yes}
\newcommand{\ID}{\cellcolor{green!25}Identity}
\newcommand{\PSEUDO}{\cellcolor{green!25}Pseudonym}
\newcommand{\ANON}{\cellcolor{green!50}Anonymity}
\newcommand{\NO}{\cellcolor{red!50}No}
\newcommand{\TTP}{\cellcolor{red!50}TTP}
\newcommand{\BC}{\cellcolor{green!50}BC}
\caption{Comparision of related works}
\label{tab:comparision}
\setlength{\tabcolsep}{3pt}

\ifx\JOURNAL\JOURNALIEEE
\begin{tabular}{|p{40pt}|p{35pt}|p{40pt}|p{35pt}|p{30pt}|p{30pt}|}
\else
\begin{tabular}{|c|c|c|c|c|c|}
\fi
\hline
Protocol & Fair exchange & Anonymity & Dispute resolution & Trust & Physical delivery \\
\hline
Alaraj, 2012~\cite{mohammedalarajFairnessPhysicalProducts2012} & \YES & \NO & \YES & \TTP & \YES \\
\hline
Bîrjoveanu, 2015~\cite{birjoveanuAnonymityFairexchangeEcommerce2015} & \YES & \YES & \NO & \TTP & \YES \\
\hline
Hinarejos et al., 2019~\cite{hinarejosSolutionSecureCertified2019} & \YES & \NO & \NO & \BC & \NO \\
\hline
Themis~\cite{mengThemisDecentralizedEscrow2019} & \YES & \NO & \YES & \BC & \NO \\
\hline
Lelantos~\cite{altawyLelantosBlockchainBasedAnonymous2017} & \YES & \PSEUDO & \NO & \BC & \YES \\
\hline
This paper & \YES & \YES & \YES & \BC & \YES \\
\hline

\end{tabular}
\end{table}

@@

Examples of blockchains that natively support confidential transactions are: Monero~\cite{vansaberhagenCryptoNote2013} (via Ring Signatures~\cite{noetherRingSignatureConfidential2015} and Bulletproofs~\cite{bunzBulletproofsShortProofs2018}), ZCash~\cite{ben-sassonZerocashDecentralizedAnonymous2014} (via zkSNARK~\cite{ben-sassonSNARKsVerifyingProgram2013}), and Grin~\cite{fuchsbauerAggregateCashSystems2019} (via Mimblewimble~\cite{jedusorMIMBLEWIMBLE2016}).

@@

The detailed description of each step and the justification %JS proof lub justification ?
of the outcome position is given in Appendix~\ref{app:proof-of-fairness}.

@@

\noindent%
\begin{minipage}{\linewidth}% to keep image and caption on one page
\makebox[\linewidth]{%        to center the image
\includegraphics[height=0.95\textheight,keepaspectratio]{anonser-experiment1.pdf}}
\captionof{figure}{Steps of the experiment, first part.}\label{fig:anonser-experiment1}%      only if needed  
\end{minipage}

\noindent%
\begin{minipage}{\linewidth}% to keep image and caption on one page
\makebox[\linewidth]{%        to center the image
\includegraphics[height=0.95\textheight,keepaspectratio]{anonser-experiment2.pdf}}
\captionof{figure}{Steps of the experiment, second part.}\label{fig:anonser-experiment2}%      only if needed  
\end{minipage}
\subsection{Results}

>>>>

\section{Introduction}
\label{sec:introduction}
Lawyers, laboratories, auditors or banks, in order to provide services, require data often containing sensitive personal information.

@@

The problem amplifies when personal information is linked to health records, or legal documents, or biological materials like DNA, saliva, or blood.

@@

The guarantee of privacy of personal data is often based solely on trust in the SPs' staff and the security of their IT systems. However, we observe that personal data is often only used for logistical purposes, such as payments or communications, and could be provided anonymously if such methods were available.

It would be desirable for the customers to keep their identities private while still receiving the service. This could lead to reduced trust that customers have to put in SPs and less responsibility borne by SPs.

@@

@@

\item Individuals undertaking entrepreneurial activities may wish to obtain estimates of the risks and possible repercussions of the actions taken.

By exposing their identity they trust that the lawyer will not use that information for harmful actions.
\end{itemize}

In this work we explore the possibilities of providing services anonymously.

@@

Our review indicates that none of the current systems is sufficient to achieve the desired goal. We propose a anonymous protocol for provisioning serivces that require physical materials. In case of dispute, either due to exceeding deadlines or providing an incorrect result, the customer can disclose the whole interaction and prove to justice the misbehavior of the SP.

To achieve these objectives, we use:
\begin{itemize}
    \item \textbf{Blockchain} (aka message board), to achieve fairness, i.e., as a means for proving that certain actions took place at a certain time without the trusted third party (TTP).
    \item \textbf{Anonymous payment methods}, like cash or anonymous cryptocurrencies, allowing customers to pay for services anonymously.
    \item \textbf{Decentralized storage network} (e.g., IPFS) to anonymously provide results together with a provable storage network (e.g., Filecoin) to guarantee that the results are available to the customer even if the SP refuses to share the result.

    \item Cryptography:
    \begin{itemize}
        \item \textbf{Symmetric encryption}, to encrypt and decrypt results published on the public networks.
        \item \textbf{Public-key cryptography}, and \textbf{Diffie-Helman key exchange (DHKE)} to derive shared secrets for symmetric encryption.
        \item \textbf{Digital signatures}, to achieve authentication and non-repudiation of actions. 
    \end{itemize}

@@

%\paragraph{Contributions}
%We contribute to the state of the art by:
The contribution of our paper is:
\begin{itemize}
\item proposing a novel protocol that:
  \begin{itemize}
  \item allows \textbf{anonymous} service provision, i.e., the service provider does not need to collect any personal information from the customer.
  \item achieves \textbf{fairness} by carefully designing the protocol as an interactive non-cooperative game, in which the SP remains in an advantageous position and the customer in a disadvantageous position with an option to start a dispute in case a misbehaviour of SP.
  \item \textbf{does not rely on centralized TTP}, but uses decentralized blockchain and distributed content-addressable storage network.
  \item In conflict-free transactions does not require customers to interact with the blockchain, achieving better \textbf{user-experience and practicality}.
  \item allows the \textbf{delivery of physical materials}, which was rarely addressed by other researchers or based on strong and unpractical assumptions.
  \item guarantees the \textbf{remote availability of the results}, even in case of the SP denial of service.
  \end{itemize} 
\item Systemise often misused definitions of anonymity, pseudonymity, linkability, and traceability.
\item Proposing a framework for analyzing fairness in fair-exchange protocols.
\item Discuss the possible improvements to the protocol with the use of secure computation, self-sovereign identities, zero-knowledge proofs, and blockchain-based dispute resolution techniques.
\end{itemize}

@@

%\paragraph{Organisation}
The rest of this paper is organized as follows.
In Section~\ref{sec:related-works} we review related works. 
Then, in Section~\ref{sec:building-blocks} we discuss the building blocks of a dispute resolution system, blockchain as a message board, fairness, anonymous payments, storage network, results availability, and anonymity.
Section~\ref{sec:protocol} provides detailed description of the protocol.
Section~\ref{sec:fairness-analysis} provides a fairness analysis of the proposed protocol.
In Section~\ref{sec:experiments} we present the implementation of the protocol and results of our experiments.
Section~\ref{sec:discussion} discuss possible improvements in terms of crowd-sourced dispute resolution or dispute avoidance, self-sovereign identities (SSI), anonymous delivery, and formal verification.
Finally, Section~\ref{sec:conclusion} concludes the paper.

\section{Related Works}\label{sec:related-works}
In this section, we review related works on fair exchange, anonymous, and physical delivery protocols. Then we outline the main differences between the protocols.

\subsection{Fair exchange, physical delivery}
The most common application of fair exchange protocols is e-commerce. A typical transaction involves a seller and a buyer who exchange money for a physical product. To protect themselves the seller want to receive the funds prior to sending the product, while the buyer want to receive the product prior to paying. The fairness of the protocol should guarantee that either both parties obtain the goods, or they both obtain nothing.

@@

@@

\ifdefstring{\FORMAT}{\DOUBLECOLUMN}{\begin{table*}}{\begin{table}}
% \ifx\FORMAT\DOUBLECOLUMN
% \begin{table*}
% \else
% \begin{table}
% \fi
\centering
\newcommand{\YES}{\cellcolor{green!50}Yes}
\newcommand{\ID}{\cellcolor{green!25}Identity}
\newcommand{\PSEUDO}{\cellcolor{green!25}Pseudonym}
\newcommand{\ANON}{\cellcolor{green!50}Anonymity}
\newcommand{\NO}{\cellcolor{red!50}No}
\newcommand{\TTP}{\cellcolor{red!50}TTP}
\newcommand{\BC}{\cellcolor{green!50}BC}
\caption{Comparision of related works.}
\label{tab:comparision}
\setlength{\tabcolsep}{3pt}

\ifdefstring{\FORMAT}{\DOUBLECOLUMN}{\begin{tabular}{|c|c|c|c|c|c|}}{\begin{tabular}{|c|c|c|c|c|c|}}

% \begin{tabular}{|p{40pt}|p{35pt}|p{40pt}|p{35pt}|p{30pt}|p{30pt}|}

\hline
Protocol & Fair exchange & Anonymity & Dispute resolution & Trust & Physical delivery \\
\hline
Alaraj, 2012~\cite{mohammedalarajFairnessPhysicalProducts2012} & \YES & \NO & \YES & \TTP & \YES \\
\hline
Bîrjoveanu, 2015~\cite{birjoveanuAnonymityFairexchangeEcommerce2015} & \YES & \YES & \NO & \TTP & \YES \\
\hline
Hinarejos et al., 2019~\cite{hinarejosSolutionSecureCertified2019} & \YES & \NO & \NO & \BC & \NO \\
\hline
Themis~\cite{mengThemisDecentralizedEscrow2019} & \YES & \NO & \YES & \BC & \NO \\
\hline
Lelantos~\cite{altawyLelantosBlockchainBasedAnonymous2017} & \YES & \PSEUDO & \NO & \BC & \YES \\
\hline
This paper & \YES & \YES & \YES & \BC & \YES \\
\hline

\end{tabular}

\ifdefstring{\FORMAT}{\DOUBLECOLUMN}
{\end{table*}}
{\end{table}}

@@

Examples of blockchains that natively support confidential transactions are: Monero~\cite{vansaberhagenCryptoNote2013} (using Ring Signatures~\cite{noetherRingSignatureConfidential2015} or Bulletproofs~\cite{bunzBulletproofsShortProofs2018}), ZCash~\cite{ben-sassonZerocashDecentralizedAnonymous2014} (using zkSNARK~\cite{ben-sassonSNARKsVerifyingProgram2013}), Grin~\cite{fuchsbauerAggregateCashSystems2019} (using Mimblewimble~\cite{jedusorMIMBLEWIMBLE2016}), and IronFish~\footnote{IronFish, The Privacy Platform
for web3, \url{https://ironfish.network}, \LASTVISITED} (using Sapling protocol~\cite{hopwoodZcashSaplingProtocol2022}).

@@

The detailed description of each step and the justification %JS proof lub justification ?
of the outcome positions is given in~\ref{app:proof-of-fairness}.

@@

\ifx\FORMAT\SINGLECOLUMN
\noindent%
\begin{minipage}{\linewidth}% to keep image and caption on one page
\makebox[\linewidth]{%        to center the image
\includegraphics[height=0.95\textheight,keepaspectratio]{anonser-experiment1.pdf}}
\captionof{figure}{Steps of the experiment, first part.}\label{fig:anonser-experiment1}%      only if needed  
\end{minipage}

\noindent%
\begin{minipage}{\linewidth}% to keep image and caption on one page
\makebox[\linewidth]{%        to center the image
\includegraphics[height=0.95\textheight,keepaspectratio]{anonser-experiment2.pdf}}
\captionof{figure}{Steps of the experiment, second part.}\label{fig:anonser-experiment2}%      only if needed  
\end{minipage}
\else
\begin{figure*}
  \centering
  \includegraphics[height=0.95\textheight,keepaspectratio]{anonser-experiment1.pdf}
  \caption{Steps of the experiment, first part.}\label{fig:anonser-experiment1}
\end{figure*}

\begin{figure*}
  \includegraphics[height=0.95\textheight,keepaspectratio]{anonser-experiment2.pdf}
  \caption{Steps of the experiment, second part.}\label{fig:anonser-experiment2}
\end{figure*}

\fi
\subsection{Results}
